A comprehensive framework to capture the arcana of neuroimaging analysis

### 2019-03-14 manuscript/manuscript.tex
renamed *Repository to *Repo
renamed ParameterSpec to ParamSpec

Similar to data specifications, parameter specifications are included in
the Study class by providing a list of \emph{ParameterSpec} objects to
the \emph{add\_param\_specs} class attribute. ParameterSpec objects
are initialised with a name and default value. Special parameters that
specify a qualitative change in the analysis, for example using ANTs
registration \citep{avants_reproducible_2011} instead of FSL registration
\citep{smith_advances_2004}, are specified by the \emph{SwitchSpec} subtype.
SwitchSpecs take a name, default value and a list of accepted values at
initialisation.

@@

In Arcana, repository access is encapsulated within modular
\emph{Repository} objects to enable switching between different
repositories and repository types at analysis ``application time''
(Figure \ref{fig:simple_uml}). There are currently three supported repository types, XNAT
\citep{marcus_extensible_2007}, BIDS \citep{gorgolewski_brain_2016} and a simple
``directory'' format, which are encapsulated by \emph{XnatRepository},
\emph{BidsRepository}, and \emph{DirectoryRepository} classes
respectively.

>>>>

Similar to data specifications, parameter specifications are included in
the Study class by providing a list of \emph{ParamSpec} objects to
the \emph{add\_param\_specs} class attribute. ParamSpec objects
are initialised with a name and default value. Special parameters that
specify a qualitative change in the analysis, for example using ANTs
registration \citep{avants_reproducible_2011} instead of FSL registration
\citep{smith_advances_2004}, are specified by the \emph{SwitchSpec} subtype.
SwitchSpecs take a name, default value and a list of accepted values at
initialisation.

@@

In Arcana, repository access is encapsulated within modular
\emph{Repository} objects to enable switching between different
repositories and repository types at analysis ``application time''
(Figure \ref{fig:simple_uml}). There are currently three supported repository types, XNAT
\citep{marcus_extensible_2007}, BIDS \citep{gorgolewski_brain_2016} and a simple
``directory'' format, which are encapsulated by \emph{XnatRepo},
\emph{BidsRepo}, and \emph{DirectoryRepo} classes
respectively.
